\textbf{Thomas Donnelly}\\
28515 890th Ave. \textbar{} Austin, MN 55912\\
(506) 279-9097 \textbar~tommymdonnelly@gmail.com\\
\href{https://github.com/TomTheTonk}{GitHub: TomTheTonk}
\href{http://linkedin.com/in/thomas-donnelly-429405320}{LinkedIn: Thomas
Donnelly}

\textbf{EXPERIENCE}

\textbf{Software Engineering Intern May 2023 - Aug 2023}\\
\emph{Hobu Inc., Iowa City, IA} \textbf{May 2024 - Aug 2024}

\begin{itemize}
\item
  Worked with a small team to plan and develop software utilizing LIDAR
  data.
\item
  Employed Meta's open-source neural network, Llama, to classify large
  LIDAR maps into categories such as ground, water, buildings, and
  vegetation using Python.
\item
  Developed a Slack app that returns a STAC of tiled geological maps
  stored on AWS, utilizing Terraform for architecture and Typescript for
  Lambda functions.
\end{itemize}

\textbf{Certified Nursing Assistant June 2019 -- Sept 2021}\\
\emph{Prairie Manor, Blooming Prairie, MN}

\begin{itemize}
\item
  Provided basic patient care, including feeding, personal hygiene,
  mobility assistance, and monitoring vital signs in a four-wing rural
  long-term nursing facility.
\item
  Worked as part of a team with registered nurses and 2-4 other
  certified nursing assistants.
\item
  Adapted to pandemic conditions, including state-mandated COVID
  testing, isolation protocols, and monitoring for visitors.
\end{itemize}

\textbf{EDUCATION}

\textbf{Bachelor of Computer Science May 2025}\\
\emph{Winona State University, Rochester/Winona, MN}

\begin{itemize}
\item
  Current GPA: 3.35
\item
  Coursework includes Java, software engineering principles, databases,
  SQL, and security management.
\item
  Created an Emotional Recognition software as part of a neural network
  project, achieving 60\% accuracy.
\end{itemize}

\textbf{SKILLS}

\begin{itemize}
\item
  \textbf{Programming:}~Python, Java, Typescript, Swift
\item
  \textbf{Cloud Services:}~Amazon Web Services (AWS)
\item
  \textbf{Development Tools:}~Terraform, Lambda
\item
  \textbf{Specialization:}~Computer Vision, GDAL
\item
  \textbf{Other:}~Teamwork, software engineering, neural networks
\end{itemize}

\textbf{REFERENCES UPON REQUEST}

\href{http://github.com/TomTheTonk/Resume}{\textbf{Document Made Using
Github Actions}}
